Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-18 paper/paper_acm.tex
adding Section 8 in plan of the paper

Section~\ref{sec:lawv-tiern-nutshell} presents an overview of the
construction.
% 
Section~\ref{sec:hott} presents the foundations of homotopy type theory
and presents a analogous of~\cite[Corollary 6.2.3.5]{lurie}. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
Lawvere-Tierney sheafification functor.
%
The definitions of this paper use an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:extension-type} describes how to use this
construction to define a modality on $\Type$ from a modality on
$\HProp$.
%
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

In this section, we present how to use the sheafification modality to
define a transformation of Matrin-Löf type theory into
itself\footnote{We define the translation on Martin-Löf type theory,
  but it could also be done for CIC as well.} as it has been done for
forcing~\cite{jaber2012extending}.

>>>>

Section~\ref{sec:lawv-tiern-nutshell} presents an overview of the
construction.
% 
Section~\ref{sec:hott} presents the foundations of homotopy type theory
and presents a analogous of~\cite[Corollary 6.2.3.5]{lurie}. 
%
Section~\ref{sec:lexmod} introduces the notion of left-exact stratified
modalities, on which this paper is based.
%
Section~\ref{sec:sheaves} defines Lawvere-Tierney sheaves in homotopy
type theory.
%
Section~\ref{sec:sheafification} explains the construction of the
Lawvere-Tierney sheafification functor.
%
The definitions of this paper use an informal presentation of
homotopy type theory, working entirely inside of Univalent
Foundations. 
 %
Section~\ref{sec:extension-type} describes how to use this
construction to define a modality on $\Type$ from a modality on
$\HProp$.
%
%
Section~\ref{sec:translation} defines the translation of Matin-Löf
type theory into itself based on this modality. 
%
Section~\ref{sec:formalization} discusses the details of the
formalization in Coq using formal type theory, in particular issues
concerning universe polymorphism.
%
Finally, Section~\ref{sec:future-works} concludes on future works.

@@

In this section, we present how to use the sheafification modality to
define a transformation of Martin-Löf type theory into
itself\footnote{We define the translation on Martin-Löf type theory,
  but it could also be done for CIC as well.} as it has been done for
forcing~\cite{jaber2012extending}.
